Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2017-03-21 manuscript.tex
latest

@@

An important potential application of eco-evolutionary models close to the evolution-only end of the spectrum is improved population-genetic inference in expanding (e.g. humans) or seasonally-cycling (e.g. \textit{Drosophila}) populations \citep{bergland_14}. Current approaches treat demography and selection as separate questions, typically fitting a demographic model to data on ostensibly neutral sites, and then inferring selection against this demographic background, despite the recurrent problem that the two are confounded \citep{schrider_2016}. Eco-evolutionary models of selection may help to remedy this situation, since demography and selection are treated as inseparable, especially on shorter timescales, both simply being the outcome of patterns of births and deaths.

>>>>

\section*{•}

Current approaches to population genetic inference treat demography and selection separately, typically fitting a demographic model to data on ostensibly neutral sites, and then inferring selection against this demographic background, despite the recurrent problem that the two are confounded \citep{schrider_2016}.

in expanding (e.g. humans) or seasonally-cycling (e.g. \textit{Drosophila}) populations \citep{bergland_14}.

 Eco-evolutionary models of selection may help to remedy this situation, since demography and selection are treated as inseparable, especially on shorter timescales, both simply being the outcome of patterns of births and deaths.

@@
